Untitled

### 2023-01-01 codebook_dat.Rmd
changes based on emails by Tatum and Elise

---
title: "Codebook created on 2022-12-18 at 2022-12-18 11:40:38"
output: github_document
---

@@

## Dataset description
The data contains 20 cases and 26 variables.

>>>>

---
title: "Codebook created on 2023-01-01 at 2023-01-01 17:14:20"
output: github_document
---

@@

## Dataset description
The data contains 20 cases and 24 variables.

### 2023-01-01 manuscript/manuscript.Rmd
changes based on emails by Tatum and Elise

```{r setup, include=FALSE}
library("worcs")
library(ggplot2)
library(kableExtra)
library(DT)
library(tidySEM)
library(knitr)
library(metafor)
library(pema)
run_everything = TRUE
sensitivity = FALSE
load_data()
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)

```

@@

mods <- c("type", "ssri", "frequency", "disease", "species", "sex", "dose", 
"hed", "pretested", "group", "outcome", "usv")
cat <- names(dat)[sapply(dat, inherits, "factor")]
cat <- cat[cat %in% mods]
```

@@

```{r, eval = run_everything}
modres <- lapply(samples, function(p){
  df <- dat[dat$Sample == p, ]
  mods_cont <- mods[!mods %in% cat]

@@

  # Find ref cat
  catvars <- sapply(dfmod, class) == "factor"
  dfmod[catvars] <- lapply(dfmod[catvars], function(v){
    tab <- table(v)
    relevel(v, ref = names(tab)[which.max(tab)])
  })
  refcat <- data.frame(do.call(rbind,lapply(names(dfmod[catvars]), function(n){c(n, levels(dfmod[[n]])[1])})))
  if(nrow(refcat) > 0) names(refcat) <- c("Variable", "Reference")
  completecases <- complete.cases(dfmod)
  modmat <- model.matrix(~., dfmod)

>>>>

```{r setup, include=FALSE}
library("worcs")
library(ggplot2)
library(kableExtra)
library(DT)
library(tidySEM)
library(knitr)
library(metafor)
library(pema)
run_everything = TRUE
sensitivity = FALSE
load_data()
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
```

@@

mods <- c("ssri", "frequency", "disease", "species", "sex",
"hed", "pretested", "sih_test_type", "usv_test_type")
if(!all(mods %in% names(dat))) stop()
cat <- names(dat)[sapply(dat, inherits, "factor")]
cat <- cat[cat %in% mods]
```

@@

```{r, eval = run_everything}
refcats <- read.csv("../reference_categories.csv", stringsAsFactors = FALSE)
modres <- lapply(samples, function(p){
  df <- dat[dat$Sample == p, ]
  mods_cont <- mods[!mods %in% cat]

@@

  # Find ref cat
  catvars <- sapply(dfmod, class) == "factor"
  dfmod[catvars] <- lapply(dfmod[catvars], function(v){
    tab <- table(v)
    relevel(v, ref = names(tab)[which.max(tab)])
  })
  # refcat <- data.frame(do.call(rbind,lapply(names(dfmod[catvars]), function(n){c(n, levels(dfmod[[n]])[1])})))
  refcat <- data.frame(Variable = names(refcats)[-1],
                       Reference = unlist(refcats[refcats$sample == p, -1]))
  refcat <- refcat[refcat$Variable %in% names(dfmod[catvars]), ]
  if(nrow(refcat) > 0) names(refcat) <- c("Variable", "Reference")
  completecases <- complete.cases(dfmod)
  modmat <- model.matrix(~., dfmod)
